\documentclass{pgnotes}

\title{Power problem set}

\begin{document}

\maketitle

Attempt the following problems.
Make sure to lay out your work well and give units (where relevant).

\begin{enumerate}

  
\item
  A device requires \SI{5}{\ampere} at \SI{230}{\volt}. Determine the apparent power.

\item
  A device consumes \SI{720}{\watt} when connected to a \SI{230}{\volt} supply. Determine the apparent power.

\item
  Two devices, A and B, operate on a \SI{230}{\volt} supply.
  Device~A consumes \SI{650}{\watt} and has a power factor of 0.9.
  Device~B consumes \SI{450}{\watt} at an unknown power factor.
  Determine the apparent power.

\item
  An IT device has an apparent power requirement of \SI{750}{\watt}.
  Its real power is \SI{680}{\watt}.
  Determine:
  \begin{enumerate}
  \item Its power factor.
  \item The reactive power component.
  \end{enumerate}

\item 
  A SAN storage array consumes 1250W at 230V:
  \begin{enumerate}
  \item Find a suitable rackmount UPS from APC / Eaton for it.
  \item Estimate runtime of your chosen UPS from specifications.
  \end{enumerate}

\item
  Write a script in PowerShell (or any other language) to do some / all of the following:
  \begin{enumerate}
  \item Work out the total apparent power for a number of devices.
  \item Add in a catalogue of commonly used devices in your data centre.
  \item Select a suitable UPS from a small catalogue (e.g. 3-5).
  \end{enumerate}
  Test your script using some of the problems above.
  
\end{enumerate}

\end{document}
